Sex differences in upper limb musculoskeletal biomechanics during a lifting task

### 2020-03-26 paper/response/response.tex

    Dear Editor-in-Chief,

    Thank you for giving us the opportunity to submit a revised draft of our manuscript to Applied Ergonomics.
    We appreciate the time and effort that you, and the reviewers, have dedicated to providing your valuable feedback.
    We have incorporated changes to reflect the suggestions provided by the reviewers and have highlighted the changes within the manuscript.

    Here is a point-by-point response to the reviewers' comments and concerns.
    To simplify proofreading, we have quoted and underlined the text in yellow when an edit has been made to the original text.

    \section{Comments from Reviewer 1}\label{sec:reviewer-1}

    \begin{formal}
        The paper is very well structured;
        the figures are helpful to understand the results.
        The analysed parameters are interesting.
        The authors give supplementary information structured in Appendix.
    \end{formal}

    We would like to thank the reviewer for her/his time and insightful comments that will help us improve the article.

@@

    \begin{quote}
        "Boxplot of the relative time spent beyond a shear-compression dislocation ratio \hl{for each trial} by sex (women in red and men in blue) and mass (6~kg on the left panel and 12~kg on the right panel) with median (horizontal lines), first-third interquartile range (bars), first-third interquartile range multiplied by 1.5 times the interquartile difference [$\textrm{Q1} - 1.5 \times \textrm{IQR}; \textrm{Q2} + 1.5 \times \textrm{IQR}$] (vertical lines).
        Data beyond the end of the whiskers are considered outliers (points)."
    \end{quote}

    \begin{formal}
        Despite this, the authors conclude "in addition, women spent more time beyond a shear-compression dislocation ratio." (section 5. \textit{Discussion}, page 15) and "we have also shown that women spend more time with a high risk of humerus dislocation." (section 5.2. \textit{Kinematic, electromyographic and musculoskeletal evidences of the sex-related differences}).
        More over, using a generic model, it is supposed that the "inter-individual variability is reduced" (section 5.3. \textit{Methodological considerations}).
        With these considerations, the authors are encouraged to be less affirmative on this point.
    \end{formal}

    While the outliers rate remains low, we fully agree and we have nuanced our interpretation of this parameter given the hypotheses it is based on.

    \textit{Abstract}:
    \begin{quote}
        "In addition, women \hl{might} spend more time beyond a shear-compression dislocation ratio."
    \end{quote}

@@

    \textit{Discussion, section 5.2. Kinematic, electromyographic and musculoskeletal evidences of the sex-related differences}:
    \begin{quote}
        "We have also shown that women \hl{might} spent more time with a high risk of humerus dislocation."
    \end{quote}

    \begin{formal}
        In terms of implications, the authors give different suggestions (section 5.4. \textit{Implications}) that are already known, for example "we recommend a technique that keeps the box closer from the trunk, reduces above shoulder work, makes greater use of the lower limbs and reduces the glenohumeral joint contribution".
        The authors are encouraged to be more ambitious and give some more insights on this point taking into account the results of the study.
    \end{formal}

    We agree that the recommendations could indeed rely more on the main finding of this study which is that women generated higher muscle forces and activations than men when the box was above shoulder level --- at either 6 or 12 kg.
    As such, we added the following sentences (\textit{Implications}, page 21):

    \begin{quote}
        "In our case, these synthetic indicators \hl{reinforced known recommendations} and emphasized the importance of a proper lifting technique on musculoskeletal loads and by extension \textsc{ulmd} prevalence. [\ldots]"
    \end{quote}

@@

    \begin{quote}
        \hl{"Taken together, our studies on kinematics~{\citep{Martinez2019-mm}}, \textsc{emg}~{\citep{Bouffard2019-fd}} and musculoskeletal biomechanics suggest that it is crucial for practitioners to give a special attention to women during above-shoulder work.
        Our indicators show that the biomechanical loads are higher in women compared to men while working above shoulder, which is critical for the development of shoulder injury~{\citep{Van_der_Molen2017-sb}}.
        It would therefore be necessary to adapt workload in women working in such position."}
    \end{quote}

    \section{Comment from Reviewer 2}\label{sec:reviewer-2}

    \begin{formal}
        Thank you for such a nice manuscript.
        You have made a great contribution to the investigation of sex differences in biomechanical loads at work.
    \end{formal}

    We thank the reviewer for her/his kind words and recommendation.

@@

    \begin{formal}
        I only recommend you considering the s\textsc{emg} normalization also as a limitation, as we know that producing a real maximal contraction is something challenging.
        An underestimated MVC (particularly in women) can bias the results.
        If you have taken some special care on that issue I also recommend you reporting it in this study.
    \end{formal}

    While this study does not involve \textsc{emg} --- but rather muscle activations and forces computed by static optimization --- we agree that this is a limitation to be discussed for the results of our previous \textsc{emg} study~\citep{Bouffard2019-fd}, on which we rely to support and explain our results.
    Especially since it was not discussed in the original paper.
    Since normalized \textsc{emg} is the product of the MVC and the measured \textsc{emg}, the MVC is indeed of key importance when comparing samples from different populations --- even more so in women, who may reach different levels of voluntary activation during MVC compared to men~\citep{Ema2018-cd, Inglis2013-uq}.

### 2020-03-26 paper/main.tex
review submission

    \section{Highlights}\label{sec:highlights}
    \begin{itemize}
        \item We investigated sex differences in upper limb musculoskeletal biomechanics during a lifting task.
        \item Women generated higher muscle forces and muscle activations when the box was above shoulder level and might spend more time beyond a shear-compression dislocation ratio.
        \item Those musculoskeletal indicators can be used to evaluate work technique and estimate the underlying musculoskeletal loads.
    \end{itemize}

>>>>

    \section{Highlights}\label{sec:highlights}
    \begin{itemize}
        \item We investigated sex differences in upper limb biomechanics during a lifting task
        \item Women generated higher muscle forces and activations when working above shoulder level
        \item Women might spend more time beyond a glenohumeral shear-compression dislocation ratio
        \item Such indicators can be used to estimate the underlying musculoskeletal loads
        \item Practitioners could use those indicators to evaluate work technique
    \end{itemize}

### 2020-03-26 paper/parts/4-discussion.tex
review submission

Work-related musculoskeletal injury is a complex multi-causal phenomenon.
Our results suggest a careful consideration of sex during ergonomic interventions on overhead tasks.
With our work on kinematics, electromyography and musculoskeletal modelling, we developed new biomechanical \textsc{ulmd} risk indicators.
The development of synthetic indicators is a step towards objective quantification of exposure to physical risk factors.
They can be used to evaluate a particular work task or technique and estimate the underlying musculoskeletal loads.
They are, for example, already applied in ergonomics investigation to report the expertise-related difference during a lifting task \cite{goubault-evsn}.
In our case, these synthetic indicators emphasized the importance of a proper lifting technique on musculoskeletal loads and by extension \textsc{ulmd} prevalence.
In order to mitigate the musculoskeletal loads on the upper limb during a lifting task, we recommend a technique that keeps the box closer from the trunk, reduces above shoulder work, makes greater use of the lower limbs and reduces the glenohumeral joint contribution.
Practitioners may also consider adapting the work environment to include lighter boxes, stabilizing muscle strengthening sessions and more generally physical activity to improve muscle strength and endurance.
These incentives are particularly recommended for female workers to compensate for the strength differential compared to men.
Taken together, our studies on kinematics~\citep{Martinez2019-mm}, \textsc{emg}~\citep{Bouffard2019-fd} and musculoskeletal biomechanics suggest that it is crucial for practitioners to give a special attention to women during above-shoulder work.
Our indicators show that the biomechanical loads are higher in women compared to men while working above shoulder, which is critical for the development of shoulder injury~\citep{Van_der_Molen2017-sb}.
It would therefore be necessary to adapt workload in women working in such position.
Beyond sex-related differences, we defend an ergonomic practice based on a process tailored to each worker and based on multidisciplinary scientific works.

>>>>

Work-related musculoskeletal injury is a complex multi-causal phenomenon.
Our results suggest a careful consideration of sex during ergonomic interventions on overhead tasks.
With our work on kinematics, electromyography and musculoskeletal modelling, we developed new biomechanical \textsc{ulmd} risk indicators.
The development of synthetic indicators is a step towards objective quantification of exposure to physical risk factors.
They can be used to evaluate a particular work task or technique and estimate the underlying musculoskeletal loads.
They are, for example, already applied in ergonomics investigation to report the expertise-related difference during a lifting task~\cite{goubault-evsn}.
In our case, these synthetic indicators reinforced known recommendations and emphasized the importance of a proper lifting technique on musculoskeletal loads and by extension \textsc{ulmd} prevalence.
In order to mitigate the musculoskeletal loads on the upper limb during a lifting task, we recommend a technique that keeps the box closer from the trunk, reduces above shoulder work, makes greater use of the lower limbs and reduces the glenohumeral joint contribution.
Practitioners may also consider adapting the work environment to include lighter boxes, stabilizing muscle strengthening sessions and more generally physical activity to improve muscle strength and endurance.
These incentives are particularly recommended for female workers to compensate for the strength differential compared to men.
Taken together, our studies on kinematics~\citep{Martinez2019-mm}, \textsc{emg}~\citep{Bouffard2019-fd} and musculoskeletal biomechanics suggest that it is crucial for practitioners to give a special attention to women during above-shoulder work.
Our indicators show that the biomechanical loads are higher in women compared to men while working above shoulder, which is critical for the development of shoulder injury~\citep{Van_der_Molen2017-sb}.
It would therefore be necessary to adapt workload in women working in such position.
Beyond sex-related differences, we defend an ergonomic practice based on a process tailored to each worker and based on multidisciplinary scientific works.
